### 2020-04-21 final_report/data.tex
add section on standardisation

\subsection{Preprocessing}
\label{sec:preprocessing}

TODO
\begin{enumerate}
	\item discrete feature embedding
	\item standardisation
\end{enumerate}

>>>>

Since some methods applied in this work are not scale-invariant or
perform suboptimally when presented with arbitrarily scaled problems, all results
produced in the sampling runs were standardised prior to further use. In this
commonly used statistical procedure, features and regression outputs are
independently scaled and offset to attain zero mean and unit variance.
